%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.2 (3/28/15)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute 
% (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Modified by:
% Daniel L Marks <xleafr@gmail.com> 3/28/2015
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%-------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%-------------------------------------------------------------------------------

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% You can have multiple style options the legal options ones are:
%
%   centered:	the name and address are centered at the top of the page 
%				(default)
%
%   line:		the name is the left with a horizontal line then the address to
%				the right
%
%   overlapped:	the section titles overlap the body text (default)
%
%   margin:		the section titles are to the left of the body text
%		
%   11pt:		use 11 point fonts instead of 10 point fonts
%
%   12pt:		use 12 point fonts instead of 10 point fonts
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[margin]{res}  

% Default font is the helvetica postscript font
\usepackage{helvet}

% Increase text height
\textheight=700pt

\begin{document}

%-------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%-------------------------------------------------------------------------------
\name{Jaysh Todi}

% Note that addresses can be used for other contact information:
% -phone numbers
% -email addresses
% -linked-in profile

\address{\\jayshtodi14@gmail.com\\jaysh.22bce8227@vitapstudent.ac.in}
\address{\\+919588269704\\Sikar,Rajasthan-332001}

% Uncomment to add a third address
%\address{Address 3 line 1\\Address 3 line 2\\Address 3 line 3}
%-------------------------------------------------------------------------------

\begin{resume}

%-------------------------------------------------------------------------------
%	EDUCATION SECTION
%-------------------------------------------------------------------------------
\section{EDUCATION}
\textbf{Vellore Institute of Technology-AP}, CSE Student with\\ Spcialization in A.I and M.L\hfill GPA: 
8.61
\\
\\
\textbf{Vidhya Bharti Public School}, June 2021\hfill 
84.40
\\
\\
\textbf{St. Mary's Sr. Sec. School}, June 2019\hfill 
 86.20
%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
%	PROJECTS SECTION
%-------------------------------------------------------------------------------
\section{EXTRA CRICULAR}
\par
\textbf{Madhya Bharat Association(Club)} : \textbf{Treasuer}\\
 Responsible for managing finances, including budgeting, keeping accurate records of transactions, and overseeing fundraising activities.\\Ensured compliance with financial policies and legal requirements, contributing to the club’s financial stability and effective operation.

\par
\textbf{Team Next Nexus Club} : \textbf{Social Media Lead} 
\par
Developed and executed social media strategies to enhance the club’s online presence and engagement. Managed content creation, scheduling, and analytics across various platforms. Coordinated with team members to ensure consistent messaging and branding. Monitored social media trends and metrics to optimize campaign effectiveness and increase follower engagement.
 

%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
%	SKILLS SECTION
%-------------------------------------------------------------------------------
\section{SKILLS}

\textbf{Finance}: Financial Modeling, Financial Analysis, Balance Sheet Review, Financial Forecasting.
\\
\textbf{Technical Skills}: Python, Java, ML, SQL, Data Science.
\\
\textbf{Soft Skills}: Problem Solving, Communication, Leadership, Effective Time Management.
\\
%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
%	PROJECTS SECTION
%-------------------------------------------------------------------------------
% Modify the format of each position
\begin{format}
\title{l}\employer{r}\\
\dates{l}\location{r}\\
\body\\
\end{format}
%-------------------------------------------------------------------------------

\section{PROJECTS}
\title{\textbf{EMG Controlled Robotic Arm}}
\employer{\textbf{ HMI Engineer}}
\begin{position}
Developed and integrated an intuitive Human-Machine Interface (HMI) for an EMG Controlled Robotic Arm, focusing on real-time signal processing, user-centered design, and seamless system integration. Collaborated with cross-functional teams to ensure usability, performance, and compliance with medical device standards, while continuously refining the interface based on user feedback and rigorous testing.
\end{position}

\employer{\textbf{Developer}}
\title{\textbf{Personal Finance Dashboard}}
\begin{position}
Designed and implemented a personal finance dashboard using Python and Excel to help users track and manage their finances. The dashboard allowed users to input and categorize their expenses, income, and savings. The project helped users analyze their financial habits, set budgetary goals, and monitor their progress, leading to more informed financial decisions..
\end{position}

\employer{\textbf{Financial Analyst}}
\title{\textbf{Investment Portfolio Optimization}}
\begin{position}
 Built an optimization model to allocate assets in a diversified investment portfolio. The model used historical return data, risk metrics, and constraints such as budget and risk tolerance to optimize the portfolio’s performance. The result was a portfolio that maximized returns while minimizing risk.
\end{position}

%-------------------------------------------------------------------------------
%	Interests
%-------------------------------------------------------------------------------
\section{INTEREST}
Financial Markets Analysis, Stock Market, Data Analysis, Reading
%-------------------------------------------------------------------------------
\end{resume}
\end{document}
